---
title: "Multi100_Huijts_EurSocioRev_2013_OY3B"
output: html_document
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

# Hypotesis to analyze

_The disadvantage in psychological well-being of childless people is smaller in countries with tolerant norms towards childlessness (p. 32)_

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(readxl)
library(lmerTest)
library(broom)
library(broom.mixed)
library(ggbeeswarm)
library(performance)
library(sjPlot)
library(marginaleffects)

theme_set(theme_light())

```

# Reading the data

We made a few changes in the dataset before analysis.  
- We created a centered version of age (and age^2) to avoid structural multicollinearity.
- We set the baseline levels for factor variables.
- We found a small rounding error in a small number of cases in `childless_disapp_std` values for Slovenia that we corrected. In the original dataset, it seemed like as Slovenia having two slightly different values for this variable, although each country should have only one value.

```{r}
edu_levels <- c("Primary", "Lower secondary", "Upper secondary", "Teritary", "Missing")

wb <- 
  read_csv(here("data/SRD Huijts data final.xls")) %>% 
  mutate(gender = recode(gndr, `1` = "Male", `2` = "Female"),
         # Create centered age (to avoid multicollinearity) and age^2
         age_ctd = scale(agea, scale = FALSE) %>% as.numeric(),
         age_ctd2 = age_ctd^2,
         # Set education baseline to Primary, set explicit NA
         edu = fct_explicit_na(edu, na_level = "Missing") %>% 
               fct_relevel(edu_levels),
         paredu = fct_relevel(paredu, edu_levels),
         # Set parental status baseline to living with children
         par_stat = fct_relevel(par_stat, "Living w children"),
         # Correcting a rounding error for country: SI
         childless_disapp_std = if_else(cntry == "SI", 0.1954625, childless_disapp_std)
         )
```


# Finding the proper random structure
We compared the fixed model (multiple linear regression without random components), the random intercept model, and random and slopes model. 

```{r}

# Non-multilevel model
wb_0 <-
  lm(wellbeing ~ age_ctd + age_ctd2 + married + edu + paredu + rel + pdwrk + 
       brncntr + sclmeet + par_stat * childless_disapp_std + gender, data = wb)

# Random intercept model
wb_int <-
  lmer(wellbeing ~ age_ctd + age_ctd2 + married + edu + paredu + rel + pdwrk + 
       brncntr + sclmeet + par_stat * childless_disapp_std + gender +
       (1 | cntry), data = wb)

# Ranndom intercept and slopes model
wb_intslope <-
  lmer(wellbeing ~ age_ctd + age_ctd2 + married + edu + paredu + rel + pdwrk + 
       brncntr + sclmeet + par_stat * childless_disapp_std + gender +
       (1 + par_stat | cntry), data = wb)
     
anova(wb_int, wb_0, wb_intslope)

```

We used the BIC for comparison, as we wanted to the the large number of predictors 

values the random intercept model is the best fit, as it 

```{r}
wb_lmer <- 
  wb %>% 
  # select(wellbeing,
  #        Age = age_ctd, 
  #        `Age square` = age_ctd2,
  #        `Marital status` = married,
  #        `Educational level` = edu,
  #        `Educational level of parents` = paredu,
  #        `Religious attendance` = rel,
  #        `Paid employment` = pdwrk,
  #        `Born in country` = brncntr,
  #        `Parental status` = par_stat,
  #        Country = cntry,
  #        `Disapproval of childlessness` = childless_disapp_std,
  #        `Social contacts` = sclmeet) %>% 
  group_by(gender) %>% 
  nest() %>% 
  ungroup() %>% 
  mutate(model = map(data, 
                     ~lmer(
                       wellbeing ~ age_ctd + age_ctd2 + married + edu + paredu + 
                                   rel + pdwrk + brncntr + sclmeet + 
                                   par_stat * childless_disapp_std + 
                                   (1 | cntry),
                       data = .x)), 
         model_tidy = map(model, tidy, conf.int = TRUE))

wb_lmer %>% 
  pull(model) %>% 
  set_names(pull(wb_lmer, gender)) %>% 
  tab_model(
          dv.labels = c("Male", "Female"),
          show.std = TRUE,
          show.est = FALSE,
          show.se = TRUE,
          show.reflvl = TRUE, 
          show.ci = FALSE,
          show.aic = TRUE,
          show.dev = TRUE,
          prefix.labels = "varname")

isSingular(wb_lmer$model[[1]])
isSingular(wb_lmer$model[[2]])

# wb_lmer$model[[1]]@vcov_beta %>% row.names() %>% sort()

```


```{r}
#Visualize results
# Separate linear regressions by country by gender
wb_lm <- 
  wb %>% 
  group_by(country = cntry, gender, childless_disapp_std) %>% 
  nest() %>% 
  mutate(model = map(data, 
                      ~lm(wellbeing ~ par_stat + age_ctd + age_ctd2 + married + 
                                      edu + paredu + rel + pdwrk + brncntr +
                                      sclmeet,
                                      data = .x)),
         model_tidy = map(model, tidy, conf.int = TRUE),
         n = map_int(data, nrow))

wb_lm %>% 
    unnest(model_tidy) %>% 
    ungroup() %>% 
    filter(str_detect(term, "par_stat")) %>% 
    select(childless_disapp_std:country, term, estimate, n) %>% 
    ggplot() +
    aes(x = childless_disapp_std, y = estimate, color = term, group = term) +
    geom_point(aes(size = n), alpha = .5) +
    geom_smooth(method = "lm", mapping = aes(weight = n), se = FALSE) + 
    geom_text(aes(label = country), check_overlap = TRUE, color = "black") +
    facet_wrap(~gender) +
    labs(title = "Association between effect size (beta) of pariatal status and well-being and childlessness disapproval",
         subtitle = "Effects are in comparison with living with children. Lines show weighted regressions.",
         x = "Childlessness disapproval",
         y = "Effect of parental status on well-being",
         color = "Parental status")
```

Childlessness disapproval is negatively associated well-being in childless females, compared to those living with children. 

We did not find this association in males. However 


# SANDBOX
```{r}


wb %>% 
  group_by(count)
  ggplot() +
  aes(x = childless_disapp_std, y = wellbeing, color = par_stat) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") + 
  facet_wrap(~gender)
  
  
wb1 <-   
  wb_lmer %>% 
  slice(1) %>% 
  pull(model) %>% 
  .[[1]]

wb %>% count(par_stat)

predictions(wb1)
wb
pred <- predictions(
    wb1,
    newdata = datagrid(cntry = NA,
                       par_stat = c("Living w children","Childless", "Empty nest"),
                       childless_disapp_std = seq(-1.5, 2, .5)),
    re.form = NA)

datagrid(
  model = wb1,
  cntry = unique(wb$cntry),
  par_stat = c("Childless", "Empty nest"),
  childless_disapp_std = seq(-1.5, 2, .5)
)

pred %>%
  ggplot() +
  aes(x = childless_disapp_std,
      y = predicted,
      group = par_stat,
      ymin = conf.low,
      ymax = conf.high) +
  geom_ribbon(alpha = .1, fill = "red") +
  geom_line() +
  # facet_wrap( ~ par_stat, labeller = label_both) +
  labs(title = "Population-level trajectories")



pred <- predictions(wb1)

ggplot(pred) +
  aes(
    x = childless_disapp_std,
    y = predicted,
    level = par_stat,
    group = par_stat
  ) +
  geom_line() +
  ylab("Predicted Weight") #+
    # facet_wrap(~ Diet, labeller = label_both)

count_pred <- 
  predictions(
    wb1,
    newdata = datagrid(cntry = unique, par_stat = unique))


cntry_pred <-
  marginalmeans(model = wb1, 
                by = c("par_stat"), 
                variables_grid = list("childless_disapp_std" = seq(-1.5, 2, .5))
                                                   ) %>% 
  filter(term == "cntry")


cntry_pred %>% 
  ggplot() +
  aes(x = childless_disapp_std, y = marginalmean, color = value, group = value)+
    geom_point(aes(size = n), alpha = .5) +
    geom_smooth(method = "lm", mapping = aes(weight = n), se = FALSE) + 
    geom_text(aes(label = country), check_overlap = TRUE, color = "black") +
    facet_wrap(~gender) +
    labs(title = "Association between effect size (beta) of pariatal status and well-being and childlessness disapproval",
         subtitle = "Effects are in comparison with living with children. Lines show weighted regressions.",
         x = "Childlessness disapproval",
         y = "Effect of parental status on well-being",
         color = "Parental status")




```



